biology

### 2020-07-23 documents/introduction.tex
Reworked paper slightly
Slide 1 done!

@@

The direct inactivation plaque and PCR data in the referenced papers are somewhat convincing corroboration that this effect is not an artifact; but hundreds of convincing and wrong papers exist in the literature.\\

@@

	Please consider all claims with appropriate skepticism.

@@

>>>>

\documentclass[paper.tex]{subfiles}
\begin{document}

@@

The direct inactivation plaque and PCR data in the referenced papers are a somewhat convincing corroboration that this effect is not a thermal artifact; but hundreds of convincing and wrong papers exist in the literature.\\

We discuss some possible artifacts in the supplemental, but nothing seems plausible. It should be noted that all three papers that reference this technique use similar methods to determine the resonance mode.\\

Then again, our incredulity is itself probably unfounded. The data these papers provide are excellent; they passed peer-review in Nature Srep, which is a far closer scrutiny than we could possibly provide.

@@

In essence, please consider all claims with appropriate skepticism.

@@

\end{document}

### 2020-07-23 documents/supplemental.tex
Slide 1 done!

Contrary to some [Hardell 2017] reports, we do not find the FCC and ICNIRP to be significantly affected by special interest groups; their rationales appear to be transparent.  [FCC-19-126A1] an FCC memorandum wherein the FCC tells groups to respectfully screw themselves no fewer than three times: ''Similarly, IEEE-ICES urges the Commission to
adopt a higher SAR exposure limit of 2 W/kg averaged over 10 g. [snip] We are not persuaded that the IEC standard should be adopted at this time.", "Medtronic and the AAMI-CRMD recommend a more relaxed threshold of 20 mW. We decline to increase the 1-mW threshold.".

@@

\PRLsep{{\itshape Fluidics }}

@@

We originally planned on using techniques from the rapidly accelerating field of centrifugal microfluidics, using a broadband patch antenna smaller than the cuvette, and measuring transmission absorption.

@@

>>>>

Contrary to some [Hardell 2017] reports, we do not find the FCC and ICNIRP to be significantly affected by special interest groups; their rationales appear to be transparent.  [FCC-19-126A1], for instance, is a particularly entertaining memorandum:

\begin{quote} 
Similarly, IEEE-ICES urges the Commission to adopt a higher SAR exposure limit of 2 W/kg averaged over 10 g. [snip] We are not persuaded that the IEC standard should be adopted at this time.", "Medtronic and the AAMI-CRMD recommend a more relaxed threshold of 20 mW. We decline to increase the 1-mW threshold.".

@@

\PRLsep{{\itshape Microfluidics: small channels, big headaches }}

@@

We originally planned on using techniques from the rapidly accelerating field of centrifugal microfluidics, using a broadband patch antenna smaller than the cuvette, and measuring transmission through the cuvette.

@@

The final process was as follows:

Just using a single-sided tape over micromachined channels didn't work for us; the tape remains sticky and stuck to the bottom of the channel, blocking it.

\begin{itemize}
	\item 1/16" 003 size Viton O-rings McMaster-Carr \#9464K103, 
	\item 3M 467MP 0.051 mm double-sided adhesive transfer tape with 200MP acrylic adhesive, DigiKey 3M9726-ND.
	Various other tapes were tried, such as 9495MP; the laser was not powerful enough to cut these.
	While the intermittent temperature rating is over 121 C, the high-pressure steam environment does seem to degrade any exposed regions of tape.

	A CO2 laser is usually used to cut these otherwise transparent materials. We only had a diode laser. However, the front and back paper liners absorb sufficient laser power to melt the tape between. This produces horrible results, but was sufficient for this purpose. With our 2.5 W, ~0.15 mm spot size, 450 mm/min for the tape.

	\item MG Chemicals 416-T Laser Printer Transparency Film, 0.1 mm thick. Presumably a PET/Mylar material.

	\item A vinyl cutter was used to cut the openings in the top mylar cover slip.
	\item Cover plate machined from polycarbonate with a 1/16" two-flute carbide endmill, 24000 RPM, between 500 and 1000 mm/min, up to 1.5 mm step-down. G-code generated with MeshCAM. This seems to withstand the autoclave without any damage.
	\item Note: the tape preferentially sticks to the back liner, rather than the front.
	Rub the thing hard with a 
	Aluminum foil

\end{itemize}

Making this device ourselves was a grave mistake that cost many lives. We should have used \cite{Straight}, a COTS version which we discovered halfway through.

I'm sorry.

\printbibliography[title={General fluidics resources}, keyword={microfluidics}]

\printbibliography[title={Centrifugal}, keyword={centrifugal}]

\PRLsep{{\itshape aaaaa }}
